\chapter{Conclusion}

\begin{TempText}
	(Max 5 pages)
\end{TempText}

% ====================================================================================

\section{Final Results}

\begin{TempText}
	@Note: In this chapter, first provide a summary of your final results including screenshots from your final game. Comment on any significant changes from the alpha release.
\end{TempText}

% ====================================================================================

\section{Experience}

\begin{TempText}
	@Note: Here you should provide commentary about your experience during the class. How well did your initial design ideas materialize into the final game. Were you able to follow your development schedule, or did you deviate significantly from it? How did the different elements of the project structure (development schedule, prototype, playtesting, etc.) contribute to or hinder your progress?
\end{TempText}

% ====================================================================================

\section{Personal Impressions}

\begin{TempText}
	@Note: Did it meet your expectations? Are you happy and proud of your game? Do you feel there wasn't enough time or that the schedule was too compressed?
\end{TempText}

\begin{TempText}
	@Note:  You might also consider these questions:
	\begin{itemize}
		\item What was the biggest technical difficulty during the project? \\
		\item What was your impression of working with the theme? \\
		\item Do you think the theme enhanced your game, or would you have been happier with total freedom? \\
		\item What would you do differently in your next game project? \\
		\item What was your greatest success during the project? \\
		\item Are you happy with the final result of your project? \\ 
		\item Do you consider the project a success? \\
		\item To what extend did you meet your project plan and milestones (not at all, partly, mostly, or always)? \\
		\item What improvements would you suggest for the course organization? (Perhaps in D1 evaluation)? \\
		\item Did you like using MonoGame?
	\end{itemize}
\end{TempText}

